A Relaxation Approach to Feature Selection \newline for Linear Mixed-Effects Models

### 2023-05-09 presentation/phd_defense_pres.tex
Isolated conference and thesis presentations to enable different style of presenting; connect Jim's math macroses and thesis's bibliography; address warnings

@@

Examples: 
\begin{itemize}
	\item $R(x) = \lambda\sum_{j=1}^p w_j\|x_j\|_1$ -- LASSO and Adaptive LASSO penalties \cite{Bondell2010,Lin2013}
	\item $R(x) = \lambda \|x\|_0$ -- $\ell_0$ penalty \cite{Vaida2005,Jones2011}
	\item $R(x)$ -- SCAD penalty (\cite{Fan2001,Fan2012})
\end{itemize}

@@

\begin{frame}{$\ell_0$-based Covariate Selection for Bullying Study from GBD}
	\begin{figure}
		\includegraphics[width=\textwidth]{Figures/bullying_data_assessment_selection.pdf}
		\caption{Fixed and random covariate selection for Bullying dataset from~\cite{GBD}. The model selected 9 covariates, 7 of which were historically significant, and did not select 4 covariates, 1 of which was historically significant.}
	\end{figure}
\end{frame}

@@

>>>>

\documentclass[8pt]{beamer}
\input{useful_packages}
\input{math_macros}

% \usetheme[progressbar=frametitle]{metropolis}
\usepackage{appendixnumberbeamer}

% PRESETS OF PACKAGES AND MATH %

\usepackage{xspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lmodern}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
\title{Physics-Informed Neural ODEs (PINODE)}
\date{\today}
\author{Aleksei Sholokhov, Steven Brunton, J. Nathan Kutz, Hassan Mansour, Saleh Nabi }
%\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}

\begin{document}

\maketitle

\begin{frame}{TODOs}
\end{frame}

\section{Introduction}
\begin{frame}{Plan of the Defense}
Show topics and published papers. Mention covid

@@

Examples: 
\begin{itemize}
	\item $R(x) = \lambda\sum_{j=1}^p w_j\|x_j\|_1$ -- LASSO and Adaptive LASSO penalties \cite{Krishna2008,Lin2013}
	\item $R(x) = \lambda \|x\|_0$ -- $\ell_0$ penalty \cite{Vaida2005,Jones2011}
	\item $R(x)$ -- SCAD penalty (\cite{Fan2001,Fan2012})
\end{itemize}

@@

\begin{frame}{$\ell_0$-based Covariate Selection for Bullying Study from GBD}
	\begin{figure}
		\includegraphics[width=\textwidth]{Figures/bullying_data_assessment_selection.pdf}
		\caption{Fixed and random covariate selection for Bullying dataset\footnote{Institute for Health Metrics and Evaluation (IHME). Bullying Victimization Relative Risk Bundle GBD 2020. Seattle, United States of America (USA), 2021.}. The model selected 9 covariates, 7 of which were historically significant, and did not select 4 covariates, 1 of which was historically significant.}
	\end{figure}
\end{frame}

@@

\section{Reduced-Order Models}
\subsection{Intro to Reduced-Order Models (ROMs)}

\begin{frame}{Reduced-Order Models}

Schematics, terminology, notation

\begin{frame}{Variations of ROMs}
	Linear, nonlinear, citations
\end{frame}

\begin{frame}{Physics-Informed Loss}
Definition of Physics-informed ML.

Derivation of PI loss through chain rule.

Problem with evaluating RHS of differential equations.

Interpretation with cross-borrowing strength. 
\end{frame}

\begin{frame}{Physics-Informed Koopman Networks}
	Linear latent dynamics

	Paper

	Not a rom so not suitable for downstream tasks. 
\end{frame}

\begin{frame}{Physics-Informed Neural ODEs (PINODE)}
	Nonlinearity in latent space
	- require a lot of data
	- picky to initialization
	- good interpolation bad extrapolation	
\end{frame}

\begin{frame}{PINODE Results on Burgers}
	Add PI loss => Fixes most of the issues
	(example with Burgers)
	Points learned
	- Inform the model about unseen conditions
	Paper reference
\end{frame}

\begin{frame}{PINODE Active}
	> PIKN: "we use it and it works"
	> PINODE: "this is how you need to use it right"
	> PINODE-Active: can we use it right automatically?

	Loop scheme
\end{frame}

\begin{frame}{PINODE Active Results}
	Best result (Burgers)
\end{frame}

\begin{frame}{PINODE-CS}
	Application of the above 
	Loss and setup
\end{frame}

\begin{frame}{PINODE-CS Results}
	Results on Burgers
	Maybe results on a harder problem
\end{frame}

\begin{frame}{References}
	\textbf{References}: 
	\bibliographystyle{plain}
	\bibliography{../bibliography.bib}
\end{frame}

\end{document}

### 2023-05-09 presentation/pysr3_conference.tex
Isolated conference and thesis presentations to enable different style of presenting; connect Jim's math macroses and thesis's bibliography; address warnings

\usepackage{xspace}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{lmodern}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
\title{Physics-Informed Neural ODEs (PINODE)}
\date{\today}
\author{Aleksei Sholokhov, Steven Brunton, J. Nathan Kutz, Hassan Mansour, Saleh Nabi }
%\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}

@@

\begin{frame}{TODOs}
\end{frame}

\section{Introduction}
\begin{frame}{Plan of the Defense}
Show topics and published papers. Mention covid

\section{Linear Mixed-Effect Models}
\subsection{ Mixed-Effects Models}
\begin{frame}{Feature Selection for Mixed-Effect Models}

@@

Examples: 
\begin{itemize}
	\item $R(x) = \lambda\sum_{j=1}^p w_j\|x_j\|_1$ -- LASSO and Adaptive LASSO penalties \cite{Krishna2008,Lin2013}
	\item $R(x) = \lambda \|x\|_0$ -- $\ell_0$ penalty \cite{Vaida2005,Jones2011}
	\item $R(x)$ -- SCAD penalty (\cite{Fan2001,Fan2012})
\end{itemize}

@@

\begin{frame}{$\ell_0$-based Covariate Selection for Bullying Study from GBD}
	\begin{figure}
		\includegraphics[width=\textwidth]{Figures/bullying_data_assessment_selection.pdf}
		\caption{Fixed and random covariate selection for Bullying dataset\footnote{Institute for Health Metrics and Evaluation (IHME). Bullying Victimization Relative Risk Bundle GBD 2020. Seattle, United States of America (USA), 2021.}. The model selected 9 covariates, 7 of which were historically significant, and did not select 4 covariates, 1 of which was historically significant.}
	\end{figure}
\end{frame}

@@

\section{Reduced-Order Models}
\subsection{Intro to Reduced-Order Models (ROMs)}

\begin{frame}{Reduced-Order Models}

Schematics, terminology, notation

\begin{frame}{Variations of ROMs}
	Linear, nonlinear, citations
\end{frame}

\begin{frame}{Physics-Informed Loss}
Definition of Physics-informed ML.

Derivation of PI loss through chain rule.

Problem with evaluating RHS of differential equations.

Interpretation with cross-borrowing strength. 
\end{frame}

\begin{frame}{Physics-Informed Koopman Networks}
	Linear latent dynamics

	Paper

	Not a rom so not suitable for downstream tasks. 
\end{frame}

\begin{frame}{Physics-Informed Neural ODEs (PINODE)}
	Nonlinearity in latent space
	- require a lot of data
	- picky to initialization
	- good interpolation bad extrapolation	
\end{frame}

\begin{frame}{PINODE Results on Burgers}
	Add PI loss => Fixes most of the issues
	(example with Burgers)
	Points learned
	- Inform the model about unseen conditions
	Paper reference
\end{frame}

\begin{frame}{PINODE Active}
	> PIKN: "we use it and it works"
	> PINODE: "this is how you need to use it right"
	> PINODE-Active: can we use it right automatically?

	Loop scheme
\end{frame}

\begin{frame}{PINODE Active Results}
	Best result (Burgers)
\end{frame}

\begin{frame}{PINODE-CS}
	Application of the above 
	Loss and setup
\end{frame}

\begin{frame}{PINODE-CS Results}
	Results on Burgers
	Maybe results on a harder problem
\end{frame}

\begin{frame}{References}
	\textbf{References}: 
	\bibliographystyle{plain}
	\bibliography{../bibliography.bib}
\end{frame}

>>>>

\usepackage{xspace}
\usepackage{caption}
\usepackage{subcaption}
\newcommand{\themename}{\textbf{\textsc{metropolis}}\xspace}
\newcommand{\ouralgo}{\ensuremath{\mathcal{MSR}3}}
\title{A Relaxation Approach to Feature Selection \newline for Linear Mixed-Effects Models}
\date{\today}
\author{Aleksei Sholokhov, James V. Burke, Peng Zheng, Damian Santomauro, and Aleksandr Aravkin}
\titlegraphic{\includegraphics[width=0.5\textwidth]{Figures/UW_amath.pdf}\hspace{3em}\includegraphics[height=1cm]{Figures/IHME_Logo.jpg}}

@@

% pysr3 part
\section{Linear Mixed-Effect Models}
\subsection{ Mixed-Effects Models}
\begin{frame}{Feature Selection for Mixed-Effect Models}

@@

Examples: 
\begin{itemize}
	\item $R(x) = \lambda\sum_{j=1}^p w_j\|x_j\|_1$ -- LASSO and Adaptive LASSO penalties \cite{Bondell2010,Lin2013}
	\item $R(x) = \lambda \|x\|_0$ -- $\ell_0$ penalty \cite{Vaida2005,Jones2011}
	\item $R(x)$ -- SCAD penalty (\cite{Fan2001,Fan2012})
\end{itemize}

@@

\begin{frame}{$\ell_0$-based Covariate Selection for Bullying Study from GBD}
	\begin{figure}
		\includegraphics[width=\textwidth]{Figures/bullying_data_assessment_selection.pdf}
		\caption{Fixed and random covariate selection for Bullying dataset from~\cite{GBD}. The model selected 9 covariates, 7 of which were historically significant, and did not select 4 covariates, 1 of which was historically significant.}
	\end{figure}
\end{frame}

@@

\begin{frame}{References}
	\textbf{References}: 
	\bibliographystyle{plain}
	\bibliography{bibliography.bib}
\end{frame}

### 2023-05-09 presentation/useful_packages.tex
Isolated conference and thesis presentations to enable different style of presenting; connect Jim's math macroses and thesis's bibliography; address warnings

% % =============== Listings ============
\usepackage{listings} % Main package for inserting code
\usepackage[scaled]{beramono} % For using the beramono font
% % =============== Algorithms ===============
\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e} % Allows for algorithm description
\usepackage[noend]{algpseudocode}
% =============== Other ===============
\usepackage{datetime} % Date-Time formatting
\usepackage{ulem} % For strikethrough text \st{}
\usepackage[colorinlistoftodos]{todonotes} % useful for leaving todonotes
\usepackage{textcomp} %Text Com­pan­ion fonts

@@

%%%%%%%%%%%%%%%%%
% TODO COMMANDS %
%%%%%%%%%%%%%%%%%
\usepackage[colorinlistoftodos]{todonotes} % useful for leaving todonotes
\newcommand{\hightodo}[1]{\todo[inline,backgroundcolor=red!90!yellow!80!white]{\textbf{\userId}: #1}}
\newcommand{\lowtodo}[1]{\todo[inline,backgroundcolor=blue!30!white]{\textbf{\userId}: #1}}
\newcommand{\ask}[2]{\todo[inline,backgroundcolor=Orchid!40!white]{
	\textbf{Ask #1} #2}}
\newcommand{\critical}[1]{\todo[inline, backgroundcolor=BrickRed!50!white]{\textbf{Critical:} #1}}
\newcommand{\search}[1]{\todo[inline, backgroundcolor=blue!30!white]{\textbf{Search:} #1}}
\newcommand{\edit}[1]{\todo[inline, backgroundcolor=CornflowerBlue!30!white]{\textbf{Edit:} #1}}
\newcommand{\verify}[1]{\todo[inline, backgroundcolor=Apricot!50!white]{\textbf{Verify:} #1}}
\newcommand{\experiment}[1]{\todo[inline, backgroundcolor=Green!50!white]{\textbf{Verify:} #1}}
\newcommand{\delegate}[2]{\todo[inline, background=Lavender]{\textbf{For #1:} #2}}

% Tips
\newtcolorbox{tip}{colframe=white, colback=gray!10!white}

% Mettings
\newcounter{meetingscounter}
\setcounter{meetingscounter}{1}
\newtcolorbox{meeting}[4]{colframe=white, colback=white, colbacktitle=gray!10!white, 
	coltitle=black, fonttitle=\bfseries, breakable,
	subtitle style={boxrule=0.4pt, colback=white},
	title={
		\begin{tabular}{p{2.5cm}p{2.5cm}p{2.5cm}p{2.5cm}l}
		\underline{Meeting \arabic{meetingscounter}}  &  \stepcounter{meetingscounter} \faCalendar\ #2 &  \faClockO\ #3 & \faMapMarker\ #4 & \faUsers\ #1
		\end{tabular}
		}
	}

>>>>

% % =============== Listings ============
\usepackage{listings} % Main package for inserting code
\usepackage[scaled]{beramono} % For using the beramono font
% % =============== Algorithms ===============
\usepackage[linesnumbered,lined,boxed,commentsnumbered]{algorithm2e} % Allows for algorithm description
\usepackage[noend]{algpseudocode}
% =============== Other ===============
\usepackage{datetime} % Date-Time formatting
\usepackage{ulem} % For strikethrough text \st{}
\usepackage{textcomp} %Text Com­pan­ion fonts

@@
